Effective Vaccination Strategies for an H1N1 Epidemic in Ithaca, New York

### 2015-09-30 final_submission/manuscript.tex
updated manuscript template

\section{Introduction}
	//TODO
\section{Model Assumptions}
	//TODO
\section{Parameter Values and Their Justifications}
	//TODO
\section{Simulation Algorithms}
	//TODO
\section{Model Predictions}
	//TODO
\section{Validation and Robustness Testing}
	//TODO
\section{Strengths and Weaknesses}
	//TODO
\section{Future Work}
	//TODO
\section{Conclusions}
	//TODO
\section{References}
	//TODO
\section{Appendix A}
	//TODO
\section{Appendix B}
	//TODO
\section{Individual Contributions}
	//TODO

>>>>

\section{Introduction}
	For this project, we were tasked with modeling a H1N1 outbreak in Ithaca, New York. The goal of this effort was to provide local government officials with a recommended plan for distributing 4000 vaccines among the city's approximately 60000 inhabitants. The strategies that officials are particularly interested in are:
	\begin{itemize}
		\item[1.]
			Focus vaccination efforts on more connected individuals
		\item[2.]
			Focus vaccination efforts on more frail or susceptible individuals
	\end{itemize}
	They wanted to know which strategy would be better under two possible scenarios:
	\begin{itemize}
		\item[1.]
			An outbreak of the H1N1 virus
		\item[2.]
			An outbreak of a new H1N1 strain that is twenty times as deadly
	\end{itemize}
	When evaluating possible strategies, we considered the following two metrics:
	\begin{itemize}
		\item[1.]
			Total number of deaths
		\item[2.]
			Total number of person-months of infection
	\end{itemize}
	Therefore, a particular distribution of vaccines is considered better if it saves more lives and prevents more suffering.

\section{Deterministic Model}
\subsection{Algorithm}

\subsection{Assumptions and Parameter Justifications}
	//TODO
\subsection{Predictions}
	//TODO
\subsection{Validation and Robustness Testing}
	//TODO
\subsection{Strengths and Weaknesses}
	//TODO
\subsection{Future Work}
	//TODO

\section{Stochastic Model}
\subsection{Algorithm}
	//TODO
\subsection{Assumptions and Parameter Justifications}
	//TODO
\subsection{Predictions}
	//TODO
\subsection{Validation and Robustness Testing}
	//TODO
\subsection{Strengths and Weaknesses}
	//TODO
\subsection{Future Work}
	//TODO

\section{Conclusions}
	//TODO
\section{References}
	//TODO
\section{Source Code}
	//TODO
\section{Individual Contributions}
	//TODO
